Response to the Reviewers' Comments

### 2018-07-30 draft/draft.tex
Final again.
Include Grant ACK in this version.

Fig.~\ref{fig:framework_proposed} illustrates the rapid energy-aware electric vehicle synthesis flow. 
Following the flow in Fig.~\ref{fig:framework_proposed}, the algorithm extracts the required acceleration, top speed and driving range, which become hard constraints for the synthesis. The algorithm finds an electric vehicle powertrain configuration that fulfills the requirements while consuming the least amount of energy for the dedicated driving mission. 
We first compute $E_{generic}$ for a given customer-dependent driving profile, \textcolor{red}{\textit{i.e.} the  vehicle speed trace over time or distance resultant from both road condition and driver's habits (harsh and frequent braking, rapid acceleration, etc.)} This requires running a vehicle simulator, but this is just one-time evaluation unlike the conventional method. The iterative steps basically are the same as the design space exploration like the conventional method by changing the motor power rating, gearbox ratio and the battery capacity discovering the resultant vehicle performance, energy consumption and the driving range. As we already computed the generic energy consumption, the iterative step simply requires multiplication operations instead of running the vehicle simulator. This drastically reduces the computation time. Once again, the resultant energy consumption, the driving range and the required battery capacity to satisfy the driving range are not the OEM standard values but the true customer-dependent values optimized for the given driving mission.

>>>>

Fig.~\ref{fig:framework_proposed} illustrates the rapid energy-aware electric vehicle synthesis flow. 
Following the flow in Fig.~\ref{fig:framework_proposed}, the algorithm extracts the required acceleration, top speed and driving range, which become hard constraints for the synthesis. The algorithm finds an electric vehicle powertrain configuration that fulfills the requirements while consuming the least amount of energy for the dedicated driving mission. 
We first compute $E_{generic}$ for a given customer-dependent driving profile, \textcolor{red}{\textit{i.e.} the  vehicle speed trace over time or distance resultant from both road condition and driver's habits (harsh and frequent braking, rapid acceleration, etc.) Derivation of $E_{Generic}$ still requires running a vehicle simulator but only once unlike the conventional methods that iteratively run the vehicle simulator.} The iterative steps basically are the same as the design space exploration like the conventional method by changing the motor power rating, gearbox ratio and the battery capacity discovering the resultant vehicle performance, energy consumption and the driving range. As we already computed the generic energy consumption, the iterative step simply requires multiplication operations instead of running the vehicle simulator. This drastically reduces the computation time. Once again, the resultant energy consumption, the driving range and the required battery capacity to satisfy the driving range are not the OEM standard values but the true customer-dependent values optimized for the given driving mission.

### 2018-07-30 response to reviewers/letter.tex
Final again.
Include Grant ACK in this version.

Fig.~6 illustrates the rapid energy-aware electric vehicle synthesis flow. 
Following the flow in Fig.~6, the algorithm extracts the required acceleration, top speed and driving range, which become hard constraints for the synthesis. The algorithm finds an electric vehicle powertrain configuration that fulfills the requirements while consuming the least amount of energy for the dedicated driving mission. 
We first compute $E_{generic}$ for a given customer-dependent driving profile, \textcolor{red}{\textit{i.e.} the  vehicle speed trace over time or distance resultant from both road condition and driver's habits (harsh and frequent braking, rapid acceleration, etc.)} This requires running a vehicle simulator, but this is just one-time evaluation unlike the conventional method.

>>>>

Fig.~6 illustrates the rapid energy-aware electric vehicle synthesis flow. 
Following the flow in Fig.~6, the algorithm extracts the required acceleration, top speed and driving range, which become hard constraints for the synthesis. The algorithm finds an electric vehicle powertrain configuration that fulfills the requirements while consuming the least amount of energy for the dedicated driving mission. 
We first compute $E_{generic}$ for a given customer-dependent driving profile, \textcolor{red}{\textit{i.e.} the  vehicle speed trace over time or distance resultant from both road condition and driver's habits (harsh and frequent braking, rapid acceleration, etc.) Derivation of $E_{Generic}$ still requires running a vehicle simulator but only once unlike the conventional methods that iteratively run the vehicle simulator.}
